---
output:md_document
---

# Reproducible Research:Project 1
# Activity monitoring data
=============================

## Loading and preprocessing the data
```{r}
unzip("repdata_data_activity.zip")
data<-read.csv("activity.csv")
```
## Mean and Median of the total number of steps taken per day
```{r}
totalsteps<-tapply(data$steps,data$date,FUN=sum,na.rm=T)
stepsmean<-mean(totalsteps)
stepsmedian<-median(totalsteps)
```
Mean of total steps taken is `r stepsmean` and median is `r stepsmedian`

### plot
```{r}
hist(totalsteps)
```
## Average daily activity pattern

```{r}
library(ggplot2)
average<-aggregate(x=list(steps=data$steps),by=list(interval=data$interval),FUN=mean,na.rm=T)
ggplot(data=average,aes(x=interval,y=steps))+geom_line()+xlab("intervals")+ylab("steps")
```
## Total number of missing values
```{r}
missing<-is.na(data$steps)
table(missing)
```
## Replace each missing value
```{r}
fill.value <- function(steps, interval) {
    filled <- NA
    if (!is.na(steps))
        filled <- c(steps)
    else
        filled <- (average[average$interval==interval, "steps"])
    return(filled)
}
filled.data <- data
filled.data$steps <- mapply(fill.value, filled.data$steps, filled.data$interval)
```
### Mean and median of steps with Histogram
```{r}
totalsteps<-tapply(filled.data$steps,filled.data$date,FUN=sum)
mean(totalsteps)
median(totalsteps)
hist(totalsteps)
```
### Activity patterns between weekdays and weekends
```{r}
weekday.or.weekend <- function(date) {
    day <- weekdays(date)
    if (day %in% c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday"))
        return("weekday")
    else if (day %in% c("Saturday", "Sunday"))
        return("weekend")
    else
        stop("invalid date")
}
filled.data$date <- as.Date(filled.data$date)
filled.data$day <- sapply(filled.data$date, FUN=weekday.or.weekend)
averages <- aggregate(steps ~ interval + day, data=filled.data, mean)
ggplot(averages, aes(interval, steps)) + geom_line() + facet_grid(day ~ .) +xlab("5-minute interval") + ylab("Number of steps")
```